---
title: "Misc"
author: "Alan T. Arnholt"
date: "May 26, 2015"
output: html_document
---

```{r}
library(PDS)
boxplot(NESARC$AGE ~ NESARC$SEX)
library(ggplot2)
ggplot(data = NESARC, aes(x = SEX, y = AGE)) + 
  geom_boxplot() + 
  theme_bw() 
```


### Pick two constructs: Military and Education


```{r}
library(dplyr)
mydata <- tbl_df(addhealth_public4) %>% 
  filter(h4mi1 == 1 & h4mi11y < 97) %>% 
  rename(AID = aid)
MD <- left_join(mydata, AddHealth)
dim(mydata)
summary(mydata$h4mi11y)
ggplot(data = mydata, aes(x = h4mi11y)) + 
  geom_bar()
xtabs(~h4ed2, data = mydata)
summary(mydata$h4ed2)
unique(mydata$h4ed2)
ggplot(data = MD, aes(x = h4ed2)) + 
  geom_bar() +
  facet_grid(.~ h4od4)
```


### A Flipped Classroom approach to Introductory Data Science Room

[FlippedLearning.org](FlippedLearning.org)

How do students learn?  Multiple modalitites.  Watch videos and do an assessment at the end.  Weekly quizzes during lab. Students placed in groups. 

* Time on task / practice
* Making connections
* Struggle

Model the first class period.  Material to be done before class.  Get students to do the work...students need to do the prep before class.  T/R class quiz on Tuesday.  Use [https://piazza.com/](https://piazza.com/)....Have student find supplemental material they think is interesting (have others comment on) then student gets credit for contribution.  


```{r}
DS <- read.table("./data/USCOTS.txt", sep="\t", quote="\"", col.names = c("user_id", "tweet_id", "data_time", "num_retweet", "tweet_text") )
summary(DS)
DS[which.max(DS$num_retweet), ]
```

```{r}
sum(DS$num_retweet > 0)/length(DS$num_retweet)
```

```{r}
library(ggplot2)
ggplot(data = DS, aes(x = log(num_retweet))) + 
  geom_density(fill = "pink") + 
  theme_bw() 
```

####

* [http://rstudio.grinnell.edu](http://rstudio.grinnell.edu)
* [https://r.amherst.edu/apps/nhorton/sat](https://r.amherst.edu/apps/nhorton/sat)

